Reproducible Research: Peer Assessment 1
By Chuk Yong


## Loading and preprocessing the data
Show any code that is needed to load the data.
Process/transform the data (if necessary) into a format suitable for your analysis

Calculate the total number of steps taken per day.
Make a histogram of the total number of steps taken each day

```{r}
setwd("~/Desktop/Rstudio/RepData_PeerAssessment1")
Data <- read.csv("activity.csv")
totalSteps <-aggregate(steps~date,data=Data,sum,na.rm=TRUE)
hist(totalSteps$steps)
```

Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean(totalSteps$steps)
median(totalSteps$steps)
```

##What is the average daily activity pattern?

Make a time series plot (i.e. ???????????????? = "????") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
intervalSteps <- aggregate(steps~interval, Data, sum, na.rm=TRUE)
plot(steps~interval,data=intervalSteps,type="l")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
intervalSteps[which.max(intervalSteps$steps),]$interval
```

Imputing missing values

Note that there are a number of days/intervals where there are missing values (coded as ????????). The presence of missing days may introduce bias into some calculations or summaries of the data.

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with ????????s)
```{r}
sum(is.na(Data$steps))
```
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
